Using Sorghum as an outgroup to find syntenic regions in Maize: regenerating

### 2017-08-17 R/SubGenome Analysis.Rmd
Spelling

# GOTerms
***

```{r GOTerms_by_EVCode, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.width=4, fig.height=4, fig.align='center'}
Type <- c("EV-EXP","EV-COMP")
Count <- c(goAnnotations.mutated %>% filter(grepl("EV-EXP", EVCode)) %>% nrow(),
      goAnnotations.mutated %>% filter(grepl("EV-COMP", EVCode)) %>% nrow())
df = data.frame(Type,Count)
ggplot(data=df, aes(x=Type, y=Count)) +
  geom_bar(stat="identity", fill="steelblue") +
  geom_text(aes(label=Count), vjust=-0.3, size=3.5
) + labs(
  title="GOTerms by EVCode"
)
```

@@

GOTerm assignments to genes by subgenome, which takes into account the gene-GOTerm pairings and considers homeologs equivalent for the purposes of determining overlap in assignments.

>>>>

# GO Terms
***

```{r GOTerms_by_EVCode, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.width=4, fig.height=4, fig.align='center'}
Type <- c("EV-EXP","EV-COMP")
Count <- c(goAnnotations.mutated %>% filter(grepl("EV-EXP", EVCode)) %>% nrow(),
      goAnnotations.mutated %>% filter(grepl("EV-COMP", EVCode)) %>% nrow())
df = data.frame(Type,Count)
ggplot(data=df, aes(x=Type, y=Count)) +
  geom_bar(stat="identity", fill="steelblue") +
  geom_text(aes(label=Count), vjust=-0.3, size=3.5
) + labs(
  title="GO Terms by EVCode"
)
```

@@

GO Term assignments to genes by subgenome, which takes into account the gene-GO Term pairings and considers homeologs equivalent for the purposes of determining overlap in assignments.
